---
title: "Reproducibility Report: Group B Choice 2"
output:
  html_document:
    toc: true
    toc_float: true
---

-------

For this exercise, please try to reproduce the results from Experiment 1 of the associated paper (Ko, Sadler & Galinsky, 2015). The PDF of the paper is included in the same folder as this Rmd file. 

#### Methods summary: 

A sense of power has often been tied to how we perceive each other's voice. Social hierarchy is embedded into the structure of society and provides a metric by which others relate to one another. In 1956, the Brunswik Lens Model was introduced to examine how vocal cues might influence hierarchy. In "The Sound of Power: Conveying and Detecting Hierarchical Rank Through Voice," Ko and colleagues investigated how manipulation of hierarchal rank within a situation might impact vocal acoustic cues. Using the Brunswik Model, six acoustic metrics were utilized (pitch mean & variability, loudness mean & variability, and resonance mean & variability) to isolate a potential contribution between individuals of different hierarchal rank. In the first experiment, Ko, Sadler & Galinsky examined the vocal acoustic cues of individuals before and after being assigned a hierarchal rank in a sample of 161 subjects (80 male). Each of the six hierarchy acoustic cues were analyzed with a 2 (high vs. low rank condition) x 2 (male vs. female) analysis of covariance, controlling for the baseline of the respective acoustic cue.

------

#### Target outcomes: 

Below is the specific result you will attempt to reproduce (quoted directly from the results section of Experiment 1):

> The impact of hierarchical rank on speakers’ acoustic cues. Each of the six hierarchy-based (i.e., postmanipulation) acoustic variables was submitted to a 2 (condition: high rank, low rank) × 2 (speaker’s sex: female, male) between-subjects analysis of covariance, controlling for the corresponding baseline acoustic variable. Table 4 presents the adjusted means by condition. Condition had a significant effect on pitch, pitch variability, and loudness variability. Speakers’ voices in the high-rank condition had higher pitch, **F(1, 156) = 4.48, p < .05**; were more variable in loudness, **F(1, 156) = 4.66, p < .05**; and were more monotone (i.e., less variable in pitch), **F(1, 156) = 4.73, p < .05**, compared with speakers’ voices in the low-rank condition (**all other Fs < 1**; see the Supplemental Material for additional analyses of covariance involving pitch and loudness). (from Ko et al., 2015, p. 6; emphasis added)

The adjusted means for these analyses are reported in Table 4 (Table4_AdjustedMeans.png, included in the same folder as this Rmd file).

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(emmeans)

# #optional packages:
# library(psych)
library(car) # for ANCOVA
# library(compute.es) # for ANCOVA
# library(lsmeans) # for ANCOVA
```

## Step 2: Load data

```{r}
# Just Experiment 1
d <-read_csv("data/S1_voice_level_Final.csv")
# DT::datatable(d)
```

## Step 3: Tidy data

```{r}
# Having a hard time tidying the data since I'm having difficulty understanding what the variables in the df are
```

## Step 4: Run analysis

### Pre-processing

```{r}
# Same as above -- hard to preprocess when I don't understand the structure of the df
```

### Descriptive statistics

In the paper, the adjusted means by condition are reported (see Table 4, or Table4_AdjustedMeans.png, included in the same folder as this Rmd file). Reproduce these values below:

```{r}
# Pitch and pitch variability
pitch <- lm(pitch_rmean ~ plev + pitch_smean, data = d)
emmeans(pitch, ~ plev)
pitch_variability <- lm(pitch_rvar ~ plev + pitch_svar, data = d)
emmeans(pitch_variability, ~ plev)

# Loudness and loudness variability
loudness <- lm(intense_rmean ~ plev + intense_smean, data = d)
emmeans(loudness, ~ plev)
loudness_variability <- lm(intense_rvar ~ plev + intense_svar, data = d)
emmeans(loudness_variability, ~ plev)

# Resonance and resonance variability
resonance <- lm(form_rmean ~ plev + form_smean, data = d)
emmeans(resonance, ~ plev)
resonance_variability <- lm(form_rvar ~ plev + form_svar, data = d)
emmeans(resonance_variability, ~ plev)
```

### Inferential statistics

> The impact of hierarchical rank on speakers’ acoustic cues. Each of the six hierarchy-based (i.e., postmanipulation) acoustic variables was submitted to a 2 (condition: high rank, low rank) × 2 (speaker’s sex: female, male) between-subjects analysis of covariance, controlling for the corresponding baseline acoustic variable. [...] Condition had a significant effect on pitch, pitch variability, and loudness variability. Speakers’ voices in the high-rank condition had higher pitch, **F(1, 156) = 4.48, p < .05**; were more variable in loudness, **F(1, 156) = 4.66, p < .05**; and were more monotone (i.e., less variable in pitch), **F(1, 156) = 4.73, p < .05**, compared with speakers’ voices in the low-rank condition (**all other Fs < 1**; see the Supplemental Material for additional analyses of covariance involving pitch and loudness).

```{r}
# reproduce the above results here

# Pitch and pitch variability
pitch_ancova <- aov(pitch_rmean ~ plev*vsex + pitch_smean, data = d)
anova(pitch_ancova)
pitch_variance_ancova <- aov(pitch_rvar ~ plev*vsex + pitch_svar, data = d)
anova(pitch_variance_ancova)

# Loudness and loudness variability
intensity_ancova <- aov(intense_rmean ~ plev*vsex + intense_smean, data = d)
anova(intensity_ancova)
intensity_variance_ancova <- aov(intense_rvar ~ plev*vsex + intense_svar, data = d)
anova(intensity_variance_ancova)

# Resonance and resonance variability
resonance_ancova <- aov(form_rmean ~ plev*vsex + form_smean, data = d)
anova(resonance_ancova)
resonance_variance_ancova <- aov(form_rvar ~ plev*vsex + form_svar, data = d)
anova(resonance_variance_ancova)
```

# Step 5: Reflection

Were you able to reproduce the results you attempted to reproduce? If not, what part(s) were you unable to reproduce?

> I had a much harder time with reproducing these results than the one I chose for Group A. I got somewhat close to reproducing the descriptive statistics and was able to find some of the same things significant for the inferential statistics, but that was about it.

How difficult was it to reproduce your results? 

> I had a hard time with this one -- I ran into the 3 hour time limit.

What aspects made it difficult? What aspects made it easy?

> Without a codebook, I wasn't clear on what all the variables were. I didn't also understand all the details of their analysis. Like when they said that they "[controlled] for the baseline of the respective acoustic cue" I wasn't sure exactly what that meant. I didn't really know how to implement that in my analysis. Perhaps that's a common thing to do in this kind of research, and if I worked in this area it would be obvious. But for me, it wasn't.